Commutative character sheaves and geometric types for supercuspidal representations

### 2017-06-30 Geometric types.tex
Working on new Section 4

\section{Examples of Nontrivial Characters on the Derived Subgroup} \label{sec:badchar}

In this section we give two examples of characters of $G(k)$ that do not vanish on $G\der(k)$.

>>>>

\section{Geometrizing Characters Nontrivial on the Derived Subgroup} \label{sec:badchar}

If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$, Section \ref{sec:noncom} provides a \emph{local system} $\cs{L}$ that is \emph{conjugation equivariant} and satisfies $\TrFrob{}(\cs{L}) = \chi$.   In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation invariant.

\subsection{Pushforward along the Lang isogeny}

For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(x) = x^{-1}\Frob{G}(x)$.  Then the pushforward $L_! (\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.
